Interested in joining the team

### 2025-01-21 join.qmd
fix contact and add general inquiry info

Please be aware that volunteer research assistant positions are also filled on a rolling basis and as needed.

@@

If you are interested in completing your M.Sc or Ph.D in the lab, please email Dr. Carter (cartem11 [at] mcmaster [dot] ) an up-to-date curriculum vitae, unofficial academic transcripts, and a 1-page statement of research interests.

>>>>

If you are interested in joining the team, please email your completed [application form](https://raw.githubusercontent.com/cartermaclab/lab-website/master/files/2024_carterlab_undergraduate-application-form.pdf){target="_blank"}, an up-to-date curriculum vitae, and unofficial transcripts to motorlab [at] mcmaster [dot] ca. *Incomplete applications will not be reviewed.*

General inquiries regarding undergraduate opportunities in the lab can be sent to cartem11 [at] mcmaster [dot] ca.

@@

If you are interested in completing your M.Sc or Ph.D in the lab, please send 1) an up-to-date curriculum vitae, 2) unofficial academic transcripts, and 3) a 1-page statement of research interests to cartem11 [at] mcmaster [dot] ca.
